Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-18 fib2.tex
another picture

Paperclip algorithm:
\begin{center}
\includegraphics[]{pic-paperclip.pdf}
\end{center}

>>>>

Transport of an anyon can be decomposed into
moves between adjacent components of the curve
diagram,
\begin{center}
\includegraphics[]{pic-move-anyon.pdf}
\end{center}
This move is (homotopic to) equivalent to one of the following:
\begin{center}
\includegraphics[]{pic-paperclip.pdf}
\end{center}
which can be distinguished between using the
winding number. We count the number of right-hand
turns made on the curve diagram (a left-hand turn counts as $-1$).
